\textls[-0]{\thetitle}

### 2023-03-15 canonicitymodel.tex
Save.

What's more, with the above model, we can map an arbitrary closed boolean term $\goodTerm{\cdot}{t}{\cB}$ to get the result $\denotesC{\goodTerm{\cdot}{t}{\cB}}(\SubstEmp) = \sub{t}{\SubstEmp} \in \sub{\cB}{\SubstEmp} = \{\true, \false\}$, Thus $t \equiv \true \text{ or } t \equiv\false$, arriving at the basic canonicity result.

>>>>

What's more, with the above model, we can map an arbitrary closed boolean term $\goodTerm{\cdot}{t}{\cB}$ to get the result $\denotesC{\goodTerm{\cdot}{t}{\cB}}(\SubstEmp)(\star) = \star^1$ or $\star^2$, witnessing $t \equiv \true \text{ or } t \equiv\false$, arriving at the basic canonicity result.
